---
title: "Week 3 Exercises"
author: "Mitchell"
date: "July 17, 2019"
output: 
  html_document: 
    keep_md: yes
---
``` {r}
library(ggplot2)
library(tidyverse)
```

Problem 1: The second line of code, which attempts to call the object `my_variable`, uses a non-dotted "i" instead of a normal, dotted i. Therefore, the called object does not exist and R returns an error message. 

Problem 2: 
```{r}
library(tidyverse)
```
There is nothing wrong with this line of code. 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```
There is nothing wrong with this code either. 
```{r}
filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```
**I'm not sure what this R code is attempting to accomplish. The first line in this code works fine because it filters the data. The second line fails because it references variables not present in `mpg`. How can it be "tweaked" so it works as intended?**

Problem 3: The command brings up a menu containing all R keyboard shortcuts. The same menu can be accessed with Help -> Keyboard Shortcuts Help. 

Chapter 5: 
```{r}
library(nycflights13)
library(tidyverse)
```

Chapter 5.2.4 Problems

Problem 1.1, 1.4, 1.5, 1.7: 
```{r}
filter(flights, arr_delay >= 2)
filter(flights, month == 7| month == 8| month == 9)
filter(flights, dep_delay <= 0, arr_delay > 2)
filter(flights, dep_time >= 0, dep_time <= 600)
```

Problem 2
```{r}
?between()
```
The command assesses whether the assigned values in a numeric vector fall within the specified range. It could be used to simplify some of the code already written; for example, the code from problems 1.4 and 1.7 could be rewritten 
```{r}
filter(flights, between(month, 7, 9))
filter(flights, between(dep_time, 0, 600))
```

Problem 3
```{r}
summary(flights$dep_time)
```
8255 flights have a missing dep_time. **I don't know how to check and see what other variables are missing values (easily).**










