---
title: "Week 5 Exercises"
author: "Mitchell"
date: "August 6, 2019"
output: 
  html_document: 
    keep_md: yes
---

##Week 4 Exercises

```{r}
library(tidyverse)
```

###10.5 Exercises

**Problem 1**
```{r}
mt_tibble <- as_tibble(mtcars)
mt_tibble
mtcars
```
As far as I can see, the only difference between a data frame and its corresponding tibble is that each entry in the rows must be associated with a variable in a tibble. In coercing `mtcars` to tibble form, a column without a header was discarded. 

**Problem 2**

For the data frame:
```{r}
df <- data.frame(abc = 1, xyz = "a")
df
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

```{r}
df2 <- as_tibble(df)
df2
df2$x
df2[, "xyz"]
df2[, c("abc", "xyz")]
```
For the first command, the same data frame/tibble is created. For the second command, the data frame calls the entries in `df$xyz`, but the corresponding tibble does not (the call does not exactly match the column name). This could potentially be an issue with working with a data frame; a mistyped call might not be easily noticed. The third and fourth commands do the same thing for both the tibble and data frame, since the exact column names are supplied. 

**Problem 4**
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

I'm doing #4 first, because it's easier. 
```{r}
#Number 4
better <- rename(annoying, one = "1", two = "2")
better
```

Now the rest, in regular order: 
```{r}
better$one
ggplot(better, mapping = aes(x = two, y = one)) + 
  geom_point()
mutate(better, three = two/one)
```

**Problem 5**
```{r}
?enframe()
```
The command can be used to convert atomic vectors into tibbles. Another neat way of moving between different types of data!

###11.2.2 Exercises

**Problem 1**
`read_delim()` would probably work pretty well. 

**Problem 4**
```{r}
read_delim("x,y\n 1,'a,b'", delim = ",", quote = "'")
```
_OOOF_ that took a while 

**Problem 5**
`read_csv("a,b\n1,2,3\n4,5,6")`: There are more entries per row than variables, so R gets confused. 
`read_csv("a,b,c\n1,2\n1,2,3,4")`: This has the same problem; entries and variables don't match up. 
`read_csv("a,b\n\"1")`: There's an extra `\`? Also more variables than entries? Very confused about what is trying to be accomplished here. 
```{r}
read_csv("a,b\n1,2\na,b")
```
This one actually runs just fine. Having an entry be the same as a variable might be confusing, though. 
`read_csv("a;b\n1;3")`: Will not run using `read_csv`. Try `read_delim` instead, specifying `;` in the `delim` argument. 


###11.3.4 Exercises

**Problem 1**
```{r}
?locale()
```
`date_names`,`date_format`,`time_format`,`decimal_mark`,`grouping_mark`, `tz` (for time zones), and `encoding` are all major arguments for `locale`. Basically, just remember that this argument allows for shifting between regional differences in data. 

**Problem 2**
`parse_number("100,000", locale = locale(grouping_mark = ",", decimal_mark = ","))` returns an error message when executed; obviously, the grouping mark and decimal mark must be different for `parse_number` to correctly parse a number. 
```{r}
parse_number(c("100,000,", "100.000"), locale = locale(decimal_mark = ",")) 
parse_number(c("100,000,", "100.000"), locale = locale(grouping_mark = ".")) 
```

As shown above, the grouping mark becomes `.`, resulting in the parse shown above. The same result is shown when `group_mark = "."`.

**Problem 3**
The arguments alter default date and time formats. Like some of the arguments shown in `parse_date`, they allow manual setting of the date-time format. 
```{r}
parse_date("11.11.2020", locale = locale(date_format = "%m.%d.%Y"))
```

**Problem 7**
Hoo boy. 
```{r}
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"

parse_date(d1, "%B %d, %Y")
parse_date(d2, "%Y-%b-%d")
parse_date(d3, "%d-%b-%Y")
parse_date(d4, "%B %d (%Y)")
parse_date(d5, "%m/%d/%y")
parse_time(t1, "%H%M")
parse_time(t2, "%I:%M:%S %p")
```
**I think I did this last one right? It's hard to tell, since it parse correctly. What does the .12 represent**