---
title: "Week 1 Exercises and Questions"
author: "Mitchell"
date: "June 28, 2019"
output: html_document
---
Questions are **bolded**. 
###Module 3: Sequences of Numbers
```{r}
myseq <- seq(5,10,length=30)
myseq
seq(along.with=my_seq)
seq_along(my_seq)
? `along.with= x`
? `seq_along()`
```
**What is the actual function of 'along.with' and `seq_along` in the above code? Swirl never directly explained the code, and when I attempted to access the documentation, nothing came up.**
 
`length()` describes length of vector within argument 
`rep(a, times = b)` generates a vector containing all elements of `a` repeated `b` times
`rep(a, each = b)` generates a vector containing all elements of a `a` repeated `b` times, one after another


###Module 4: Vectors
>Vectors come in two different flavors: atomic vectors and lists. An atomic vector contains exactly one data type, whereas a list may contain multiple data types... numeric vectors, which are one type of atomic vector. Other types of atomic vectors include logical, character, integer, and complex.

`a <- b (logical argument such as >, <=, ==, or !=) c` creates a new logical vector `a` containing a series of logical values that compare every element in vector `b` with those of `c` as defined by the logical argument
Logical operators include `|` for union; `&` for intersection; `!A` for negation of `A`. 

`a <- c("a", "b", "c") creates a new character vector `a` with elements `"a"`, `"b"`, and `"c"`
`paste(a, collapse = "q")` pushes all elements in `a` together to print a new character vector with length 1; between every element in `a`, the condition `q` is added
*The paste function also changes all included numerical vectors into character vectors.
`paste("a", "b", "c",..., sep = "q")` pushes `"a"`, `"b"`, `"c"`, etc. together to print a new character vector with length 1; between each element, the condition `q` is added
 *If any of the combined vectors are of length greater than 1, the vectors will be combined in order in a pairwise fashion; in other words, vector recycling occurs. Example: 
```{r}
boy <- c("Big", "angry")
paste("very", boy, sep = " ")
```
 
 